A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-11-09 pilot-publication/manuscript.Rmd
Start defining basic results

# Results
Between X and X, we enrolled X trauma patients from X participating
centres. The ATLS arm enrolled X patients, the PTC arm X patients, and
the standard care arm X patients. The study flowchart is shown in
Figure X and sample characteristics across trial arms are shown in
Table X. Overall, the number of females were X (X%), the median age
was X (IQR X), and the median ISS was X (IQR X). A total of X (X%)
patients had the primary outcome of mortality at 30 days after arrival
to the emergency department.

>>>>

# Results

**Note that participating centres are randomly assigned to the
different arms every time this manuscript is compiled**

Between `r start.date` and `r end.date`, we enrolled `r n.patients`
trauma patients from `r n.centres` participating centres. The ATLS arm
enrolled `r n.atls` patients, the PTC arm `r n.ptc` patients, and the
standard care arm `r n.control` patients. The study flowchart is shown
in Figure X and sample characteristics across trial arms are shown in
Table X. Overall, the number of females were X (X%), the median age
was X (IQR X), and the median ISS was X (IQR X). A total of X (X%)
patients had the primary outcome of mortality at 30 days after arrival
to the emergency department.
